Meta-analysis

### 2020-05-26 04_MetaAnalysis.Rmd
Move impute yield error to function to reduce code in metaAnalysis Rmd

```{r imputing_variances}
# generate yield error values
for (i in 0:500) {
   # Imputing missing log variances
   log_Yerror <- rnorm(
      n = sum(is.na(slimmer_PM_dat$yield_error)),
      mean = mean(log(slimmer_PM_dat$yield_error), na.rm = TRUE),
      sd = sd(log(slimmer_PM_dat$yield_error), na.rm = TRUE)
   )

   # First let's convert Variance to standard error for all the variables that have variance recorded
   slimmer_PM_dat$yield_SE <-
      sqrt(slimmer_PM_dat$yield_error) / sqrt(slimmer_PM_dat$n)

   # Second; adding the imputed standard errors
   slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"] <-
      sqrt(exp(log_Yerror)) / sqrt(slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "n"])

   # all errorbars should overlap so they are consistant with the meta-data describing no significant difference bettween treatments
   # let's test to make sure
   if (max(outer(
      X = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      Y = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
      (2 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
      FUN = "-"
   )) > 0) {
      message(
         paste(
            "\nWarning!!: Imputed yield errors show significant differences when they should not, imputation will automatically rerun - iteration",
            "i =",
            i
         )
      )
      next()
   } else{
      message(
         paste(
            i,
            "iterations: ",
            "imputed variances now show no significant distances :)\n Now adding variances to data "
         )
      )

      # Plot the imputed errors for each trial
      Vplot <-
         slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), ] %>%
         ggplot(aes(y = grain_yield.t.ha, trial)) +
         #geom_point()+
         geom_pointrange(
            ymin = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] -
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            ymax = slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "grain_yield.t.ha"] +
               (1.95 * slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_SE"]),
            position = "jitter"
         ) +
         ylim(0.2, 1.5)

      slimmer_PM_dat[is.na(slimmer_PM_dat$yield_error), "yield_error"] <-
         exp(log_Yerror)
      print(Vplot)
      break()
   }
}
```

>>>>

```{r imputing_variances}
source("./R/impute_yield_err.R")

imputed_error_list <- impute_yield_err(slimmer_PM_dat, "grain_yield.t.ha", "yield_error","n")

slimmer_PM_dat <- imputed_error_list[["new_dataFrame"]]
